---
title: "ChocoRatings"
author: "Jeff Grayum"
date: "1/22/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Installing Libraries.
```{r}
library(tidyverse)
library(scales)
library(janitor)
library(tidytuesdayR)
library(ggthemes)
library(silgelib)
library(tidytext)
library(tidymodels)
library(textrecipes)
library(skimr)
#install.packages("LiblineaR")
library(LiblineaR)
theme_set(theme_hc())
```

Importing data.
```{r}
tuesdata <- tidytuesdayR::tt_load('2022-01-18')

chocolate <- tuesdata$chocolate

chocolate %>%
  view()
```

We will try and predict "rating" based on "most memorable characteristics"

Exploratoray data analysis.
```{r}

chocolate %>%
  ggplot(aes(rating)) +
  geom_histogram(bins = 15) +
  labs(x = "Rating",
       y = "",
       title = "Chocolate Ratings") 

tidy_chocolate <- chocolate %>%
  unnest_tokens(word, most_memorable_characteristics) %>%
  view()

tidy_chocolate %>%
  count(word, sort = TRUE)
```

Exploratory data analysis cont.
```{r}
tidy_chocolate %>%
  group_by(word) %>%
  summarize(n = n(),
            rating = mean(rating)) %>%
  ggplot(aes(n, rating)) +
  geom_hline(yintercept = mean(chocolate$rating),
                               lty = 2, color = "gray50", size = 1) +
  geom_point(color = "midnightblue", alpha = 0.7) +
  geom_text(aes(label = word), check_overlap = TRUE,
            vjust = "top", hjust = "left") +
  scale_x_log10() +
  labs(x = "Popularity (log scale)",
       y = "Rating")
```

We will now begin our modeling!
```{r}
set.seed(123)

#Process: Split, train split, test split.

#Split data is what we use to train, test, and tune.  Must consider "data budget"!
choco_split <- initial_split(chocolate, strata = rating)

choco_train <- training(choco_split)

choco_test <- testing (choco_split)

#Now create re-sampling folds from the training set (simulated versions of training set...using crossvalidation to create folds)  All from training set!
set.seed(234)
choco_folds <- vfold_cv(choco_train, strata = rating)
choco_folds
```

Let's set up our preprocessing using a recipe.
```{r}
choco_recipe <- 
  recipe(rating ~ most_memorable_characteristics, data = choco_train) %>%
  step_tokenize(most_memorable_characteristics) %>%
  step_tokenfilter(most_memorable_characteristics, max_tokens = 100) %>%
  step_tf(most_memorable_characteristics)

prep(choco_recipe) %>%
  bake(new_data = NULL) %>%
  skimr::skim()

prep(choco_recipe) %>%
  bake(new_data = NULL) %>% 
  view()
```

Three characteristics to define what a model is:
1)Algorithm (e.g., random forest, support vector machine, logistic regression)
2)The engine.  The computational engine we use to fit the model. Different R packages... carrot, spark.  We're using the defaults , here.
3) Mode.  Describes the outcome... what kind of problem we're working in. (Classification, regression...)
```{r}

ranger_spec <-
  rand_forest(trees = 500) %>%
  set_engine("ranger") %>%
  set_mode("regression")

ranger_spec

#Now we will make a support vector machine
svm_spec <- 
  svm_linear() %>%
  set_engine("LiblineaR") %>%
  set_mode("regression")

svm_spec
```

Now we will build a model workflow (encompasses preprocessing and model).
```{r}
ranger_wf <- workflow(choco_recipe, ranger_spec)
svm_wf <- workflow(choco_recipe, svm_spec)
```



```{r}
doParallel::registerDoParallel()
contrl_preds <- control_resamples(save_pred = TRUE)

svm_rs <- fit_resamples(
  svm_wf,
  resamples = choco_folds,
  control = contrl_preds
)

ranger_rs <- fit_resamples(
  ranger_wf,
  resamples = choco_folds,
  control = contrl_preds
)
```

Comparing models.
```{r}
collect_metrics(svm_rs)
collect_metrics(ranger_rs)

#Ranger is slightly better.  Rsquared is higher, RMSE is lower.  They are close! Both are actually pretty low.
```

Let's visualize the results of our regression model!
```{r}
bind_rows(
  collect_predictions(svm_rs) %>%
    mutate(mod = "SVM"),
  collect_predictions(ranger_rs) %>%
    mutate(mod = "Ranger")
  ) %>%
  ggplot(aes(rating, .pred, color = id)) +
  geom_abline(lty = 2, color = "gray50", size = 1.2) +
  geom_jitter(alpha = 0.5) +
  facet_wrap(vars(mod)) +
  coord_fixed() +
  theme(legend.position = "none")
  

```

